A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-27 article/05_Conclusion.Rmd
more love for the conclusion
reproducibility is key

Now it is time to ask

For this paper burial traditions were the main object of research, but the same methodological approach could be applied for other aspects of cultural behaviour.

>>>>

Beyond these intrinsic results, it is important now to ask what this paper means for the study of human behaviour in general. Two possible answers:

1. For this paper burial traditions were the main object of research, but the same methodological approach could be applied for other aspects of cultural behaviour reconstruction in archaeology. The idea to systematically collect data points that combine spatial and temporal location with simplified meta information about cultural phenomena might be a way to achieve better reproducibility of overarching narratives. Fast and easy *reproducibility* is of crucial importance to achieve scientific progress and it includes the notion of rather technical *preproducibility* [@starkReproducibilityMustCome2018]: Data (and code) must be shared to fuel advances archaeological theory building [@kitzesPracticeReproducibleResearch2017; @marwickComputationalReproducibilityArchaeological2017].

2. test
